---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

I will use `ggplot2` for all graphs
```{r, echo = TRUE}
library(ggplot2)
```

## Loading and preprocessing the data

Read the data from the file `activity.csv` and convert the 2nd column to the Date format
```{r, echo = TRUE}
data <- read.csv("activity.csv")
data[,2] <- as.Date(data[,2], "%Y-%m-%d")
```

## What is mean total number of steps taken per day?

### The histogram of the total number of steps taken each day
```{r, echo = TRUE}
ggplot(na.omit(data), aes(x=date, y=steps)) + geom_bar(stat='identity')
```

### The **mean** and **median** total number of steps taken per day
```{r, echo = TRUE}
mean <- with(data, aggregate(steps, list(date), mean, na.rm = TRUE))
names(mean) <- c("date", "mean")
median <- with(data, aggregate(steps, list(date), median, na.rm = TRUE))
names(median) <- c("date", "median")
merge(mean, median)
```

## What is the average daily activity pattern?

### Create a dataset  the average number of steps taken across all days on each 5 min interval
```{r, echo = TRUE}
average <- with(data, aggregate(steps, list(interval), mean, na.rm = TRUE))
names(average) <- c("interval", "steps")
```

### The time series plot the 5-minute interval and the average number of steps taken across all days
```{r, echo = TRUE}
ggplot(na.omit(data), aes(x=interval, y=steps)) + stat_summary(fun.y="mean", geom="line")
#qplot(x=interval, y=steps, data = average, geom="line")
```

### 5-minute interval that contains the maximum number of steps on average across all the days
```{r, echo = TRUE}
average[which.max(average[,2]),]
```
The interval 835 has the maximum amount of step

## Imputing missing values

### The total number of missing values in the dataset
```{r, echo = TRUE}
summary(is.na(data))
```
The total number of rows with NA is 2304

### Prepare to re-use the data frame mean to re-fill the values
```{r, echo = TRUE}
mean[is.na(mean[,2]), 2] <- 0
```

### Create a dataset equal to the original dataset but with the missing data filled in
```{r, echo = TRUE}

```

## Are there differences in activity patterns between weekdays and weekends?

### Add a factor variable indicating whether a given date is a weekday or weekend day
```{r, echo = TRUE}
data$day <- "weekday"
data[weekdays(data$date) == "Saturday" | weekdays(data$date) == "Sunday", "day"] <- "weekend"
data$day <- as.factor(data$day)
```

### Make a panel plot of the 5-minute interval (x-axis) and the average number of steps taken
### averaged across all weekday days or weekend days (y-axis)
```{r, echo = TRUE}
ggplot(na.omit(data), aes(x=interval, y=steps)) + facet_wrap(~ day, nrow = 2) + stat_summary(fun.y="mean", geom="line")
```
