---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data

Read the data from the file `activity.csv` and convert the 2nd column to the Date format
```{r, echo = TRUE}
data <- read.csv("activity.csv")
data[,2] <- as.Date(data[,2], "%Y-%m-%d")
```

## What is mean total number of steps taken per day?

### The histogram of the total number of steps taken each day
```{r, echo = TRUE}
library(ggplot2)
ggplot(na.omit(data), aes(x=date, y=steps)) + geom_bar(stat='identity')
```

### The **mean** and **median** total number of steps taken per day
```{r, echo = TRUE}
mean <- with(data, aggregate(steps, list(date), mean))
names(mean) <- c("date", "mean")
median <- with(data, aggregate(steps, list(date), median))
names(median) <- c("date", "median")
merge(mean, median)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
